Trajectories

### 2022-12-01 index.qmd
Replace colour palettes with achromatic-safe colours

```{r}
#| label: tbl-items-summary
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
#| fig-cap: "Lexical frequencies. Mean, standard error, and 95% confidence interval of lexical frequencies of items included in the Catalan and Spanish lists, reported separately for identical cognates, non-identical cognates, and non-cognates."
items <- left_join(items, select(bvqdev::pool, te, item, language, class, semantic_category))

@@

m %>% 
    ggplot(aes(x = age_std, y = .epred)) +
    facet_wrap(~.category) +
    stat_lineribbon(size = 1, colour = NA, .width = c(0.95, 0.89, 0.67, 0.5)) +
    stat_summary(fun = "mean", geom = "line", size = 0.75) +
    scale_x_continuous(
        breaks = (seq(10, 36, 4)-mean(df$age))/(sd(df$age)),
        labels = seq(10, 36, 4)
    ) +
    scale_fill_manual(
        values = rev(clrs), 
        labels = c("95%", "89%", "67%", "50%")
    ) +
    labs(
        x = "Age (months)", 
        y = "Probability of acquisition",
        colour = "Credible interval", 
        fill = "Credible interval"
    ) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    theme(
        axis.ticks.x = element_line(colour = "black"),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-phonemes
#| fig-cap: "Proportion of responses to each category by age and number of phonemes"
df %>% 
    mutate(
        age = floor(age),
        n_phon = cut_interval(n_phon, n = 4)
    ) %>%
    count(age, n_phon, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~n_phon) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    scale_y_continuous(labels = percent) +
    theme_custom() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-exposure
#| fig-cap: "Proportion of responses to each category by age and exposure."
df %>% 
    mutate(
        age = floor(age),
        exposure = cut_interval(exposure, n = 4)
    ) %>%
    count(age, exposure, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~exposure) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    scale_y_continuous(labels = percent) +
    theme_custom() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-lv
#| fig-cap: "Proportion of responses to each category by age and Levenhstein similarity"
df %>% 
    mutate(
        age = floor(age),
        lv = cut_interval(lv, n = 4)
    ) %>%
    count(age, lv, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~lv) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_fill_d3() +
    scale_y_continuous(labels = percent) +
    theme_custom() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```
:::

@@

[TO DO: emmeans tests]

@@

```{r}
#| label: fig-marginal-effect
#| fig-cap: "Average marginal effect of phonological similarity (Levenshtein distance) on the probability of comprehension and production across the range of values of exposure. The observed range of values of the word exposure index is indicated in the X-axis, and the estimated average marginal effect of phonological similarity (Levenshtein distance) is indicated in the Y-axis. This quantity is generated by averaging the derivative of the regression coefficient of the predictor Levenshtein across the range of values of all predictors but Exposure. We represent the uncertainty associated with the resulting estimate by generating multiple values of this marginal effect by drawing multiple samples from the posterior distribution of the model coefficients, calculating the average marginal effect for each posterior draw, and plotting the result as a thin grey line. Closer lines indicate lower uncertainty over the true value of the average marginal effect of Levenshein, while more distant lines indicate higher uncertainty."
nd <- datagrid(
    model = model_fit_4,
    n_phon_std = 0,
    lv_std = 0,
    exposure_std = seq_range(model_fit_4$data$exposure_std, 10),
    age_std = 0,
    id = NA,
    te = NA
)

@@

marg_effects %>% 
    posteriordraws() %>%
    as_tibble() %>% 
    filter(term=="lv_std") %>% 
    mutate(draw = draw/4) %>% 
    ggplot(aes(exposure_std, draw)) +
    geom_hline(yintercept = 0, size = 1, colour = "grey") +
    # geom_line(aes(group = drawid), alpha = 0.25, size = 0.75, colour = clrs[1]) +
    stat_summary(fun.data = median_hdi, geom = "ribbon",
                 colour = NA, alpha = 0.5, fill = clrs[1]) +
    stat_summary(fun = median, geom = "line", size = 1, color = clrs[1]) +
    labs(
        x = "Exposure index",
        y = "Marginal effect of phonological similarity\n(Levenshtein distance)"
    ) +
    scale_x_continuous(
        labels = label_number(style_positive = "plus", suffix = " SD"),
    ) +
    scale_y_continuous(
        labels = label_percent(style_positive = "plus", ),
        breaks = seq(-1, 1, 0.05)
    ) +
    theme(
        legend.position = "top",
        panel.grid = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", size = 0.75)
    )

>>>>

```{r}
#| label: tbl-items-summary
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
#| tbl-cap: "Lexical frequencies. Mean, standard error, and 95% confidence interval of lexical frequencies of items included in the Catalan and Spanish lists, reported separately for identical cognates, non-identical cognates, and non-cognates."
items <- left_join(items, select(bvqdev::pool, te, item, language, class, semantic_category))

@@

m %>% 
    ggplot(aes(x = age_std, y = .epred)) +
    facet_wrap(~.category) +
    stat_lineribbon(size = 1, colour = NA, .width = c(0.95, 0.89, 0.67, 0.5)) +
    stat_summary(fun = "mean", geom = "line", size = 0.75) +
    scale_x_continuous(
        breaks = (seq(10, 36, 4)-mean(df$age))/(sd(df$age)),
        labels = seq(10, 36, 4)
    ) +
    scale_fill_manual(
        values = rev(clrs), 
        labels = c("95%", "89%", "67%", "50%")
    ) +
    labs(
        x = "Age (months)", 
        y = "Probability of acquisition",
        colour = "Credible interval", 
        fill = "Credible interval"
    ) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    theme(
        legend.position = "top",
        axis.ticks.x = element_line(colour = "black"),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-phonemes
#| fig-cap: "Proportion of responses to each category by age and number of phonemes"
df %>% 
    mutate(
        age = floor(age),
        n_phon = cut_interval(n_phon, n = 4)
    ) %>%
    count(age, n_phon, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~n_phon) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-exposure
#| fig-cap: "Proportion of responses to each category by age and exposure."
df %>% 
    mutate(
        age = floor(age),
        exposure = cut_interval(exposure, n = 4)
    ) %>%
    count(age, exposure, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~exposure) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| lab: fig-responses-age-lv
#| fig-cap: "Proportion of responses to each category by age and Levenhstein similarity"
df %>% 
    mutate(
        age = floor(age),
        lv = cut_interval(lv, n = 4)
    ) %>%
    count(age, lv, response) %>% 
    ggplot(aes(age, n, fill = response)) +
    facet_wrap(~lv) +
    geom_col(position = position_fill()) +
    labs(x = "Age (months)", y = "Proportion of responses", fill = "Response") +
    scale_y_continuous(labels = percent) +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid = element_blank()
    )
```
:::

@@

@@

```{r}
#| label: fig-marginal-effect
#| fig-cap: "Average marginal effect of phonological similarity (Levenshtein distance) on the probability of comprehension and production across the range of values of exposure. The observed range of values of the word exposure index is indicated in the X-axis, and the estimated average marginal effect of phonological similarity (Levenshtein distance) is indicated in the Y-axis. This quantity is generated by averaging the derivative of the regression coefficient of the predictor Levenshtein across the range of values of all predictors but Exposure. We represent the uncertainty associated with the resulting estimate by generating multiple values of this marginal effect by drawing multiple samples from the posterior distribution of the model coefficients, calculating the average marginal effect for each posterior draw, and plotting the result as a thin grey line. Closer lines indicate lower uncertainty over the true value of the average marginal effect of Levenshein, while more distant lines indicate higher uncertainty."
nd <- datagrid(
    model = model_fit_4,
    n_phon_std = 0,
    lv_std = 0,
    exposure_std = seq(-1.5, 1.5, length.out = 100),
    age_std = 0,
    id = NA,
    te = NA
)

@@

marg_effects %>% 
    posteriordraws() %>%
    as_tibble() %>% 
    filter(term=="lv_std") %>% 
    mutate(draw = draw/4) %>% 
    ggplot(aes(exposure_std, draw)) +
    geom_hline(yintercept = 0, size = 1, colour = "grey") +
    # geom_line(aes(group = drawid), alpha = 0.25, size = 0.75, colour = clrs[1]) +
    stat_summary(fun.data = median_hdi, geom = "ribbon",
                 colour = NA, alpha = 0.5, fill = clrs[1]) +
    stat_summary(fun = median, geom = "line", size = 1, color = clrs[1]) +
    labs(
        x = "Word exposure index",
        y = "Marginal effect of phonological similarity\n(Levenshtein distance)"
    ) +
    scale_x_continuous(
        labels = label_number(style_positive = "plus", suffix = " SD"),
        breaks = seq(-2, 2, 0.5)
    ) +
    scale_y_continuous(
        labels = label_percent(style_positive = "plus", ),
        breaks = seq(-1, 1, 0.05)
    ) +
    theme(
        legend.position = "top",
        panel.grid = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", size = 0.75)
    )
